---
title: "EDPS 845 Assignment 1"
author: "Chansuk Kang"
---

## Overview

Demonstrate your mastery of concepts and procedures covered in *An Introduction to R*, chapters 1 through 9. See Appendix A for examples.

Complete this assignment by responding to each question below using your own original code, in addition to answering any questions. Follow Google's [R coding conventions](https://google.github.io/styleguide/Rguide.xml), and use [R markdown](http://rmarkdown.rstudio.com/index.html) formatting for your responses, with example R code written as

```{r}
# Comment within some example code
```

Your file should have an Rmd extension, and you should check that it compiles to HTML using the *Knit* command in RStudio (this runs `knitr::knit()` on the file). Note that you can already *Knit* this file to see how it works.

## Exercises

### Chapter 1

1. Show that you can access the home page for the HTML R help menu, as well as help files for individual functions.
```{r, eval=FALSE}
# whenever we need to help we type "either help() or "?""
help.start()
?
help()
?mean
```

2. Demonstrate correct and incorrect naming of R objects.

```{r,eval=FALSE}
# correct naming:
temp <- c(1,2,3,4)
temp
# [1] 1 2 3 4
# incorrect naming: the one start with numetic value:
10temp <- c(1,2,3,4)
#Error: unexpected symbol in "10temp"
#
```

3. How do you list all available objects in the R workspace? And how do you remove individual objects?

```{r, eval=FALSE}
# "ls()" can be used to display the names of (most of) the objects
ls()

# "rm()" can be used to remove objects
rm(x, y, z)
```


### Chapter 2

1. Create and index a vector using a logical, integer, negative integer, and character vector.
```{r, eval=FALSE}

## creating interger vector
x <- seq(1, 21, by = 2)
x
# [1]  1  3  5  7  9 11 13 15 17 19 21

# indexing of it
x[1:5]
# [1] 1 3 5 7 9

## creating negative interger vector
y <- seq(-10, -1)
y
#  [1] -10  -9  -8  -7  -6  -5  -4  -3  -2  -1

# indexing of it
y[-(1:5)]
# [1] -5 -4 -3 -2 -1

## creating logical vector
z <- x > 10
z
#  [1] FALSE FALSE FALSE FALSE FALSE  TRUE  TRUE
# [8]  TRUE  TRUE  TRUE  TRUE

# indexing of it
x[z]
# [1] 11 13 15 17 19 21

## Creating Character vector
labs <- paste(c("X","Y"), 1:11, sep="")
labs
# [1] "X1"  "Y2"  "X3"  "Y4"  "X5"  "Y6"  "X7" 
# [8] "Y8"  "X9"  "Y10" "X11"

# indexing of it
labs[c(1,3,5)]
# [1] "X1" "X3" "X5"
```

2. Create a simple data frame containing a numeric variable, character variable, and factor with at least 3 levels. Use the data frame to demonstrate how R codes and handles missing data. 
```{r, eval=FALSE}
x1 <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa","qld", "vic")
x2 <- round(rnorm (1:10, 10, 2), 2)
x3 <- c(0, 1, 2, 0, 1, 2, 0, 1, 2, 99)
x3f <- factor(x3)
#  [1] 0  1  2  0  1  2  0  1  2  99
#  Levels: 0 1 2 99
levels(x3f) # checking levels of x3f

dat <- data.frame(students = x1, minutes = x2, score = x3f)
dat$score[dat$score==99] <- NA # recoding values to                                  # missing data
dat
dat[!complete.cases(dat),] # checking missing data
newdat <- na.omit(dat) # creating new dataset without
                       # missing values
newdat
```

### Chapter 3

1. Demonstrate how to check and change the modes and attributes of R objects.
```{r, eval=FALSE}
z <- 1:10
mode(z) # check modes
class(z) # check class
zf <- as.factor(z) # change modes, i.e., coercion
zfi <- as.integer(zf) # change modes, z = zfi
attr(z, "dim") <- c(1, 10) # check attributes

```

### Chapter 4

1. Complete the exercise on page 17, where you calculate 95% confidence intervals for state mean incomes.
```{r, eval=FALSE}
state <- c("tas", "sa",  "qld", "nsw", "nsw", "nt",  "wa",  "wa", "qld", "vic", "nsw", "vic", "qld", "qld", "sa",  "tas","sa",  "nt",  "wa",  "vic", "qld", "nsw", "nsw", "wa","sa",  "act", "nsw", "vic", "vic", "act")
statef <- factor(state)
table(statef)
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48, 65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
data.frame(i = incomes, s = statef)
incmeans <- tapply(incomes, statef, mean)
stderr <- function(x) sqrt(var(x)/length(x))
incster <- tapply(incomes, statef, stderr)
ns <- table(statef)
cis <- data.frame(mean = incmeans, stderr = incster,
  state = names(incmeans),
  lower = qt(.025, ns - 1),
  upper = qt(.025, ns - 1, lower.tail = FALSE))
# plot
library("ggplot2")
ggplot(cis, aes(state, mean)) +
  geom_point() +
  geom_errorbar(aes(ymax = mean + stderr, ymin = mean -

```

2. In what order are the levels of ordered factors stored in?
```{r, eval=FALSE}
The levels of factors are stored in alphabetical order
ordered(statef)
levels(statef)
#[1] "act" "nsw" "nt"  "qld" "sa"  "tas" "vic"
#[8] "wa" 

```

### Chapter 5

1. Create an array with dimensions `c(3, 6, 2)` and use it to demonstrate array indexing.
```{r, eval=FALSE}
x11 <- array(1:36, dim = c(3, 6, 2))
x11[, , 1]
x11[1, , 1]
x11[2, 3, 2]
```

2. Create a two dimensional array of 100 integers sampled with replacement from the vector 1:20, and use an index array to set the diagonal values to 0.
```{r, eval=FALSE}
a1 <- array(1:20, dim = c(10,10))
i <- array(c(1:10, 1:10), dim=c(10,2))
a1[i]
a1[i] <- 0
a1
```

3. Construct the same array using the `array()` function and using a vector with the `dim()` set. Prove they are the same.
```{r,eval=FALSE}
???????
z <- array(1:36, dim=c(3,6,2))
z <- 1:36 ; dim(Z) <- c(3,6,2)
```

4. Use your array from 5.1, and another with the same dimensions, to demonstrate how arithmetic works with arrays.
```{r, eval=FALSE}
x11
x21 <- array(1:12, dim = c(3, 6, 2))
D <- 2*x11*x21 + 1
dim(D)
# [1] 3 6 2
```

5. Show how to clear the dimensions of an array.
```{r, eval=FALSE}
x11
vec <- as.factor(x11)
# [1] 1  2  3  4  5  6  7  8  9  10 11 12 13 14 15
# [16] 16 17 18 19 20 21 22 23 24 25 26 27 28 29 30
# [31] 31 32 33 34 35 36
# 36 Levels: 1 2 3 4 5 6 7 8 9 10 11 12 13 14 ...36

```

### Chapter 6

1. Demonstrate the different ways of subsetting a list.
```{r, eval=FALSE}
# say we have a list
Lst <- list(name="Fred", wife="Mary", no.children=3,
child.ages=c(4,7,9))
length(Lst) # # of components
Lst$name
# [1] "Fred"
Lst[["name"]]
# [1] "Fred"
Lst[[1]]
# [1] "Fred"

```

2. What is the difference between giving multiple lists to `list()` versus `c()`?
```{r, eval=FALSE}
# When the concatenation function c() is given list 
# arguments, the result is an object of mode
# list also, whose components are those of the 
# argument lists joined together in sequence.

Lst1 <- list(name="Chan", wife="Eun", no.children=1,
child.ages= 6)
Lst2 <- list(name="Jun", wife="Soo", no.children=1,
child.ages= 7)

list.12 <- c(Lst, Lst1, Lst2)
```

3. How do data frames in R relate to lists?
```{r, eval=FALSE}
# A data frame is a list with class "data.frame". 
# There are restrictions on lists that may be made
# into data frames: 
# Vector structures appearing as variables of the 
# data frame must all have the same length,
# and matrix structures must all have the same row 
# size.

```

4. What is the purpose of `attach()`?
```{r, eval=FALSE}
# attach() make database attached to the R search 
# path. So objects in the database can be accessed by
# giving their names.

dat
dat$score # examining a variable(score) w/o attach()
attach(dat)
score # examining a variable(score) w/ attach()
#  [1] 0    1    2    0    1    2    0    1   
#  [9] 2    <NA>
# Levels: 0 1 2 99
detach(dat)
score
# Error: object 'score' not found
```

### Chapter 7

1. Demonstrate the different approaches to reading in data from an external file.

```{r, eval=FALSE}
# 1. Load data from a r-packages
# load equate package
library("equate")
# load data
data(PISA)
std <- PISA$students

# 2. Read a csv file from a fold in desktop
setwd("C:/Users/Lindsay/Desktop/Chansuk/edps845/edps-845")
bel <- read.csv("beliefsw1.csv")

```

### Chapter 8

1. Demonstrate the use of distribution functions to simulate data and calculate probabilities and quantiles.
```{r, eval=FALSE}
a <- rnorm(1000, 10, 2)
hist(a, probability = T)
pa <- pnorm(a, 10, 2, lower.tail =T, log.p = F)
quantile(a)
qa <- qnorm(a, 10, 2, lower.tail = T, log.p = F)
```


2. Simulate data from a t distribution and check their normality.
```{r, eval=FALSE}
b <- rt(250, df = 5)
qqnorm(b) # normality check
qqline(b)
qqplot(qt(ppoints(250), df = 5), b, xlab = "Q-Q plot for t")
```

### Chapter 9

1. What is the difference between `if() else` and `ifelse()`?
```{r, eval=FALSE}
#Both of them are used in conditional execution in 
# r.'if() else' statements work on a single value at # a time, however, 'ifelse()' statements work on in # a vectorized way. Since 'ifelse()' operates on 
# vectors, it avoiding loops. In that sense, the 
# advantage of 'ifelse()' over the standard 'if 
# ()else' is that it is vectorized. Thus it's 
# potentially much faster.

# if () else
x <- c("what","is","truth")

if("Truth" %in% x) {
   print("Truth is found")
} else {
   print("Truth is not found")
}
# [1] "Truth is not found"

# ifelse()
x <- 1:10
y <- ifelse(x %% 2 == 0,5,12)  # %% is the mod operator
y
# [1] 12  5 12  5 12  5 12  5 12  5
```

2. Demonstrate the use of a `for()` loop.
```{r, eval=FALSE}
# read 13 data files using for loop function
setwd("C:/Users/Lindsay/Desktop/Chansuk/edps845/edps-845/in-class") # location of 13 csv files

for(i in 1:13)
{
  oname = paste0("test", i, sep="")
  assign(oname, read.csv(paste0(oname, ".csv", sep=""),row.names = 1))
}

ls()
test1
head(test1)
```

